02_DESeq_hyp

### 2019-04-05 analysis/02_DESeq2_hyp.Rmd
hyp and gonad
hyp deseq2

```{r}
library(tidyverse)
library(DESeq2)
library(cowplot)

@@

summary(aov(PC6 ~ treatment, data=pcadata)) 
```

>>>>

```{r}
library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)

@@

summary(aov(PC6 ~ treatment, data=pcadata)) 
```
```{r heatmap}
# see http://bioconductor.org/packages/devel/bioc/vignettes/DESeq2/inst/doc/DESeq2.html#heatmap-of-the-count-matrix
sampleDists <- dist(t(assay(vsd)))

sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- NULL
colnames(sampleDistMatrix) <- colData$treatment
colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
pheatmap(sampleDistMatrix,
         clustering_distance_rows=sampleDists,
         clustering_distance_cols=sampleDists,
         col=colors,
         fontsize = 6)
```
